\section{Brown Dwarf Mergers}

\subsection{With Brown Dwarfs}

The existence of BD-BD binary systems has been observationally well-established.  Since neither object has ever underwent steady H-fusion, common-envelope evolution cannot be used to create a close-in BD-BD system - this requires other mechanisms, such as three-body interactions, to come into play \citep{dangkr06,bearks11}.  As exactly how BD and BD systems are formed is still being debated, such a scenario cannot be ruled out \citep{bearks11}.

\cite{bearks11} has studied the merger of a BD with a 1 - 10 M$_{J}$ gas giant.  Despite the mass ratio $q$ being tiny, the density difference betwene the two objects means that a gas giant can actually approach a BD until it is tidally disrupted and forms an accretion disk, which falls onto the BD in a matter of several days.  This highly super-Eddington accretion powers the light curve.  This process is called a ``mergeburst'', and similar mergeres between main-sequence stars are covered in another section of the report.  As this process is qualitatively similar to what was described in Sec. \ref{ssec:mechanicsofwdmergers}, it might be useful in describing cold (no nuclear processing) mergers between massive and extremely light BDs.  \citeauthor{bearks11} suggests that the light curve of this mergeburst in the V-band will to first order look like a scaled-down version of other intermediate-luminosity optical transients (ILOTs), and scales the V-band light curve of V838 Mon's ILOT to the parameters of the BD to obtain \citeauthor{bearks11} Eqn. 7.  Using this same equation for a 60 M$_{J}$ - 30 M$_{J}$ BD-BD merger, we obtain a peak V-band luminosity of $10^{38}$ - $10^{39}$ erg s$^{-1}$ ($\sim$ -7 - -10 mag), and a transient timescale (from the disk's viscous timescale) of a few days.

There are several limitations with this simple scale-up from \citeauthor{bearks11} to a BD-BD merger.  For one, more equal-mass BD-BD mergers should disrupt both stars, creating a remnant hottest at its centre - subsequent disk accretion may result in enough compressional heating to ignite central burning, or the stars might even ignite during the merger.  An H-flash during accretion followed by steadier nuclear burning might also be possible in cases of unequal mass mergers (see Sec. \ref{ssec:sdbstarformationchannel} for similar evolution with He).  Lastly, any explosive event or violent accretion event should eject material, which will modify light curves.  An in-depth study of BD-BD mergers would be needed to address these issues.

\textbf{MARTEN}: My understanding is that mergebursts obtain their energy from shock-heating of material as it plows into the outer atmosphere of the accretor.  Since this also happens in WD mergers, should we expect mergerburst like emission, at least at the beginning?

\subsection{With White Dwarfs}

A number of BD-WD systems are known to exist in nature.  Observationally there is, however, a distinct lack of close-in MS-BD systems, a trend known as the ``brown dwarf desert'' \citep{stamw08}.  The most massive BDs should be $\sim 0.08$ {\Msun}, while the least massive known WDs are approximately double this value, suggesting that $q = 0.5$ BD-WD systems (unstable by the analysis in Sec. \ref{ssec:stabilityofmasstransfer}) may exist \citep{brow+11}.  Note there is extensive work on WDs stably accreting hydrogen-rich material, which is covered in other sections of this report.

%It is posited that a BD-WD system is the end result of cataclysmic variable evolution in a WD-MS binary, and therefore such systems should be, to first order, as common as CV binaries are - these systems are, however, stable to mass transfer \citep{}

Like with BD-BD mergers, our literature search did not find any studies of WD-BD mergers.