\section{Thesis Overview}

The chapters are ordered in accordance with the proposed evolution of the \citeal{vkercj10} channel.  In Chapter \ref{ch:ch2}, we consider the range of possible merger remnant configurations to arise from the parameter space of merging CO WD binaries.  In 

For the most part, I have reproduced exactly the texts of \citeal{zhu+13}, \citeal{zhu+15} and \citeal{zhu+16} in their respective chapters.  The exceptions are the chapter introductions, where I have excised certain paragraphs to eliminate the redundancy of having multiple paragraphs repeating an overview of the \citeal{vkercj10} channel.  The papers' abstracts have also been modified into chapter overviews, and certain figures reformatted for readability.  Any additional changes are noted at the start of each chapter.  Most prominently, we have added a postscript to Chapter \ref{ch:ch2} (Sec. \ref{sec:postscript_pme}) that considers our simple semi-analytical prescription for post-merger viscous evolution in light of new results, and we included an extensive appendix to Chapter \ref{ch:ch5} that details our calculation of convective suppression in magnetized, rotating WDs.

\section{The Physics of Pre-Merger Evolution}

To preface Chapter \ref{ch:ch2}, which focuses on the merger remnants, we briefly cover a few topics related to evolution of the CO WD binary leading up to mass transfer, and the early stages of mass transfer leading up to the merger proper (which we refer to as ``coalescence'').

\subsection{Stable and Unstable Mass Transfer}

In Chapter \ref{ch:ch2}, every single one of our simulated binaries merge, as we use approximate initial conditions that place unperturbed, spherical WDs at separations that guarantee immediate Roche lobe overflow.  An order of magnitude estimate, however, would suggest that binaries with sufficiently small mass ratios would not merge at all.

%http://adsabs.harvard.edu/abs/2016arXiv160404269B
%http://adsabs.harvard.edu/abs/2015ApJ...805L...6S

\subsection{Are Merging WDs Co-Rotating?}

While this question is something that we shall discuss at length in Ch. \ref{ch:ch2} (and is also considered in other works such as \cite{XXX} and \cite{ji+13}) the results of Ch. \ref{ch:ch3} suggest that it is likely unimportant for the configuration of the merger remnant (at least to first order).

Check Schwab+12 intro for synchronization links.


%http://adsabs.harvard.edu/abs/2015ApJ...815...63A
%http://adsabs.harvard.edu/abs/2016ApJ...824...46B
%https://arxiv.org/abs/1606.05292

%http://adsabs.harvard.edu/abs/2015arXiv151203442P
%http://adsabs.harvard.edu/abs/2016MNRAS.tmp..977F



%http://adsabs.harvard.edu/abs/2016ApJ...817...27W

%http://adsabs.harvard.edu/abs/2016ApJ...818...26D

%http://adsabs.harvard.edu/abs/2016arXiv160401021F
%http://adsabs.harvard.edu/abs/2016ApJ...818L..19M
