\section{Methods} 
\label{sec:c4_codes}

We employ the moving-mesh code \arepo\ \citep{spri10}, which solves the equations of ideal MHD on a Voronoi mesh coupled with self-gravity.  We operate the code in its pseudo-Lagrangian mode, so that the mesh-generating points that define the Voronoi grid move with the local velocity of the fluid.  To conserve angular momentum to within $\sim2$\% of its initial value, we use the latest improvements to time integration and gradient estimate \citep{pakm+16}.  \arepo's MHD implementation is described in \cite{pakmbs11} and \cite{pakms13}; we use the \cite{powe+99} eight-wave scheme for divergence control.  Our simulation ignores outer hydrogen and helium layers, composition gradients, and nuclear reactions (negligible for sub-\Mch\ CO WD mergers; \citealt{loreig09,rask+12}).

We model the merger of two CO WDs with masses of 0.625 and 0.65 \Msun, respectively, in a circular, unsynchronized binary with initial separation $\azero = 2.20\times10^9$ cm (corresponding period $\pzero = 49.5$ s), chosen (using the estimate of \citealt{eggl83}) such that the lower-mass WD just fills its Roche lobe.  We chose masses typical of the narrowly peaked empirical mass distribution of field CO WDs \citep{klei+13}.  Our initial conditions are very similar to those of the 0.625 - 0.65 \Msun\ binary simulated with smoothed particle hydrodynamics (SPH) in \citeauthor{zhu+13} (\citeyear{zhu+13}; henceforth \citeal{zhu+13}).  As in \citeal{zhu+13}, both WDs are generated with a uniform initial temperature of $5\times10^6$ K (the corresponding thermal pressure is dynamically irrelevant) and a uniform composition of equal parts carbon and oxygen by mass.  They are separately relaxed to hydrostatic equilibrium using the SPH code \gasoline\ \citep{wadssq04} and added to \arepo\ by converting the SPH particles to mesh-generating points while retaining their conservative quantities (mass, momentum and energy).  A uniform $10^{-5}$ \gcc\ background grid fills up a $10^{12}$ cm box centered on the binary. Each WD is given a (dynamically irrelevant) dipole seed magnetic field with an equatorial surface value of $10^3$ G (and corresponding central field of $\sim2\times10^7$ G). The fields are overlapped when the two stars are placed into a binary.

The mass resolution of our simulation is $m_\mathrm{cell} \approx 1\times10^{-6}$ \Msun.  We utilize explicit refinement and derefinement \citep{voge+12} to keep cell masses within a factor of two of $10^{-6}$ \Msun\ and to ensure adjacent cells differ by less than a factor of 10 in volume.

%comparable to the highest resolutions used in recent SPH simulations \citep{pakm+12b, rask+13}
